Supplementary Figures: Eco-evolutionary dynamics and collective migration: implications for salmon metapopulation robustness

### 2017-09-06 Manuscript/FinalDraft_rev/supp.tex
?3

\usepackage[font={small}]{caption}
\usepackage{subcaption}
\captionsetup{compatibility=false}
\usepackage{xr}
\externaldocument[extfig-]{msv4}
%\usepackage{epstopdf}
%\usepackage{array}
%\usepackage{tabularx}
%\usepackage{multirow}
\usepackage{color}
%\usepackage{multibox}
%\usepackage{rotating}
% \usepackage{lineno}

@@

\begin{figure}
  \captionsetup{justification=raggedright,
singlelinecheck=false
}
\centering
\includegraphics[width=0.35\textwidth]{figs2/fig_relax_small.pdf}
\caption{
Extinction of low-density population with a high constant straying rate $m=0.4$ and low trait heritability $h^2=0.2$ (see figure \ref{extfig-fig:relax}a).
Black line marks the calculated point of recovery post-perturbation.
Trait optima are $\theta_1 = 10$ (blue population trajectory) and $\theta_2 = 5$ (red population).
} \label{fig:relaxtraj_ldlh}
\end{figure}

\begin{figure}
  \captionsetup{justification=raggedright,
singlelinecheck=false
}
\centering
\includegraphics[width=0.35\textwidth]{figs2/fig_relax_large.pdf}
\caption{
Extinction of high-density population with a high straying rate $m=0.4$ and low trait heritability $h^2=0.2$ (see figure \ref{extfig-fig:relax}a).
Black line marks the calculated point of recovery post-perturbation.
Trait optima are $\theta_1 = 10$ (blue population trajectory) and $\theta_2 = 5$ (red population).
} \label{fig:relaxtraj_hdlh}
\end{figure}
% 
% \begin{figure}
%   \captionsetup{justification=raggedright,
% singlelinecheck=false
% }
% \centering
% \includegraphics[width=0.35\textwidth]{figs2/fig_relax_small_highh.pdf}
% \caption{
% Extinction of low-density population with a high constant straying rate $m=0.4$ and high trait heritability $h^2=0.8$ (see figure \ref{fig:relax}a).
% Black line marks the calculated point of recovery post-perturbation.
% Trait optima are $\theta_1 = 10$ (blue population trajectory) and $\theta_2 = 5$ (red population).
% } \label{fig:relaxtraj_ldhh}
% \end{figure}
% 
% \begin{figure}
%   \captionsetup{justification=raggedright,
% singlelinecheck=false
% }
% \centering
% \includegraphics[width=0.35\textwidth]{figs2/fig_relax_large_highh.pdf}
% \caption{
% Extinction of high-density population with a high straying rate $m=0.4$ and high trait heritability $h^2=0.8$ (see figure \ref{fig:relax}a).
% Black line marks the calculated point of recovery post-perturbation.
% Trait optima are $\theta_1 = 10$ (blue population trajectory) and $\theta_2 = 5$ (red population).
% } \label{fig:relaxtraj_hdhh}
% \end{figure}

\begin{figure*}
  \captionsetup{justification=raggedright,
singlelinecheck=false
}
\centering
\includegraphics[width=0.9\textwidth]{figs2/fig_relax_highh.pdf}
\caption{
Recovery time of $N_T$ following the extinction of either the low-density (light gray) or high-density (gray) population, or the near-collapse of both (dark gray) assuming (a) constant straying rates $m$ and (b) density-dependent straying rates (evaluated at the steady state $m^*$) with trait heritability $h^2=0.8$.
If $m$ is density-dependent, in the alternative stable state regime there are two straying rates observed: one each for the low- and high-density populations, respectively, which are linked by a horizontal line.
} \label{fig:relax_highh}
\end{figure*}

\begin{figure}
  \captionsetup{justification=raggedright,
singlelinecheck=false
}
\centering
\includegraphics[width=0.4\textwidth]{figs2/fig_thetadiffN.pdf}
\caption{
Median difference in population densities taken over the straying rate as a function of habitat heterogeneity $\Delta\theta$.
Solid lines are for constant $m$; dashed lines are for density-dependent $m$} \label{fig:thetadiffN}
\end{figure}

\begin{figure*}
  \captionsetup{justification=raggedright,
singlelinecheck=false
}
\centering
\includegraphics[width=0.8\textwidth]{figs2/fig_relaxtheta2.pdf}
\caption{
(a) Recovery time after near collapse of both populations as a function of straying rate $m$ and habitat heterogeneity $\Delta\theta$.
(b) The same as (a) but including recovery times when straying is density-dependent, shown by linked pairs of points.
Recovery times for systems with density-dependent straying are longer at low straying rates and shorter at higher straying rates, mirroring the change in portfolio effects shown in figure \ref{extfig-fig:thetaPE}.
} \label{fig:relaxtheta}
\end{figure*}

\begin{figure}
  \captionsetup{justification=raggedright,
singlelinecheck=false
}
  \centering
  \includegraphics[width=0.35\textwidth]{figs2/fig_MDPE_hm_mtheta_rt.pdf}
  \caption{
  Distance dependent portfolio effects as a function of straying rate $m$ and trait heritability $h^2$. When straying is distance dependent, $m$ increases as $\Delta\theta$ decreases.
  } \label{fig:mthetaPE}
\end{figure}

\begin{figure}
  \captionsetup{justification=raggedright,
singlelinecheck=false
}
\centering
\includegraphics[width=0.35\textwidth]{figs2/fig_relax_inertia.pdf}
\caption{
Distance dependent straying, where increased differences in trait optima between sites $\Delta\theta$ corresponds to lower rates of straying $m$.
At low rates of straying $m=0.02$ ($\Delta\theta=24$), extinction of the dominant population leads to slower-than-expected recovery times because the subordinate population is isolated enough to evolve towards its own trait optimum. %until growth of the dominant population overwhelms this local selection.
In this case, $m$ is less than $m=0.034$ (denoted by the asterisk in figure \ref{extfig-fig:mtheta}), such that isolation allows the subdominant population to `run away' from the influence of the dominant population, leading to a switch in states.
If $m$ is low but greater than $0.034$, isolation permits the subdominant population to `run away' from the influence of the dominant population, until it is overwhelmed by the recovering dominant population, and reverts back to its previous trait mean prior to the disturbance.
} \label{fig:inertia}
\end{figure}

\begin{figure*}
  \captionsetup{justification=raggedright,
singlelinecheck=false
}
  \centering
  \includegraphics[width=0.8\textwidth]{figs2/fig_relax_mtheta.pdf}
  \caption{
  Distance dependent recovery times for three disturbance types. When straying is distance dependent, $m$ increases as $\Delta\theta$ decreases for constant (a) and density-dependent (b) staying rates.
  The fold bifurcation is not as clear in (b) because $\Delta\theta$ is a function of the individual straying rate $m_0$, whereas the x-axis in (b) is the straying rate at the steady state $m^*$.
  Despite this difference, the general trends shown in (a) are also present in (b).
  } \label{fig:mthetamvm}
\end{figure*}

\begin{figure}
  \captionsetup{justification=raggedright,
singlelinecheck=false
}
\centering
\includegraphics[width=0.35\textwidth]{figs2/fig_relax_both_lowh.pdf}
\caption{
Near collapse of both populations with a low straying rate $m=0.1$ and low trait heritability $h^2=0.2$ (see figure \ref{extfig-fig:relax}a).
Black line marks the calculated point of recovery post-perturbation.
Trait optima are $\theta_1 = 10$ (blue population trajectory) and $\theta_2 = 5$ (red population).
} \label{fig:relaxtraj_bothlh}
\end{figure}

>>>>

\usepackage[font={small}]{caption}
\usepackage{subcaption}
\captionsetup{compatibility=false}
\usepackage{xr}
\externaldocument[extfig-]{msv5}
%\usepackage{epstopdf}
%\usepackage{array}
%\usepackage{tabularx}
%\usepackage{multirow}
\usepackage{color}
%\usepackage{multibox}
%\usepackage{rotating}
% \usepackage{lineno}

@@

\begin{figure}
  \captionsetup{justification=raggedright,
singlelinecheck=false
}
\centering
\includegraphics[width=0.35\textwidth]{fig_relax_small.pdf}
\caption{
Extinction of low-density population with a high constant straying rate $m=0.4$ and low trait heritability $h^2=0.2$ (see figure \ref{extfig-fig:relax}a).
Black line marks the calculated point of recovery post-perturbation.
Trait optima are $\theta_1 = 10$ (blue population trajectory) and $\theta_2 = 5$ (red population).
} \label{fig:relaxtraj_ldlh}
\end{figure}

\begin{figure}
  \captionsetup{justification=raggedright,
singlelinecheck=false
}
\centering
\includegraphics[width=0.35\textwidth]{fig_relax_large.pdf}
\caption{
Extinction of high-density population with a high straying rate $m=0.4$ and low trait heritability $h^2=0.2$ (see figure \ref{extfig-fig:relax}a).
Black line marks the calculated point of recovery post-perturbation.
Trait optima are $\theta_1 = 10$ (blue population trajectory) and $\theta_2 = 5$ (red population).
} \label{fig:relaxtraj_hdlh}
\end{figure}
% 
% \begin{figure}
%   \captionsetup{justification=raggedright,
% singlelinecheck=false
% }
% \centering
% \includegraphics[width=0.35\textwidth]{figs2/fig_relax_small_highh.pdf}
% \caption{
% Extinction of low-density population with a high constant straying rate $m=0.4$ and high trait heritability $h^2=0.8$ (see figure \ref{fig:relax}a).
% Black line marks the calculated point of recovery post-perturbation.
% Trait optima are $\theta_1 = 10$ (blue population trajectory) and $\theta_2 = 5$ (red population).
% } \label{fig:relaxtraj_ldhh}
% \end{figure}
% 
% \begin{figure}
%   \captionsetup{justification=raggedright,
% singlelinecheck=false
% }
% \centering
% \includegraphics[width=0.35\textwidth]{figs2/fig_relax_large_highh.pdf}
% \caption{
% Extinction of high-density population with a high straying rate $m=0.4$ and high trait heritability $h^2=0.8$ (see figure \ref{fig:relax}a).
% Black line marks the calculated point of recovery post-perturbation.
% Trait optima are $\theta_1 = 10$ (blue population trajectory) and $\theta_2 = 5$ (red population).
% } \label{fig:relaxtraj_hdhh}
% \end{figure}

\begin{figure*}
  \captionsetup{justification=raggedright,
singlelinecheck=false
}
\centering
\includegraphics[width=0.9\textwidth]{fig_relax_highh.pdf}
\caption{
Recovery time of $N_T$ following the extinction of either the low-density (light gray) or high-density (gray) population, or the near-collapse of both (dark gray) assuming (a) constant straying rates $m$ and (b) density-dependent straying rates (evaluated at the steady state $m^*$) with trait heritability $h^2=0.8$.
If $m$ is density-dependent, in the alternative stable state regime there are two straying rates observed: one each for the low- and high-density populations, respectively, which are linked by a horizontal line.
} \label{fig:relax_highh}
\end{figure*}

\begin{figure}
  \captionsetup{justification=raggedright,
singlelinecheck=false
}
\centering
\includegraphics[width=0.4\textwidth]{fig_thetadiffN.pdf}
\caption{
Median difference in population densities taken over the straying rate as a function of habitat heterogeneity $\Delta\theta$.
Solid lines are for constant $m$; dashed lines are for density-dependent $m$} \label{fig:thetadiffN}
\end{figure}

\begin{figure*}
  \captionsetup{justification=raggedright,
singlelinecheck=false
}
\centering
\includegraphics[width=0.8\textwidth]{fig_relaxtheta2.pdf}
\caption{
(a) Recovery time after near collapse of both populations as a function of straying rate $m$ and habitat heterogeneity $\Delta\theta$.
(b) The same as (a) but including recovery times when straying is density-dependent, shown by linked pairs of points.
Recovery times for systems with density-dependent straying are longer at low straying rates and shorter at higher straying rates, mirroring the change in portfolio effects shown in figure \ref{extfig-fig:thetaPE}.
} \label{fig:relaxtheta}
\end{figure*}

\begin{figure}
  \captionsetup{justification=raggedright,
singlelinecheck=false
}
  \centering
  \includegraphics[width=0.35\textwidth]{fig_MDPE_hm_mtheta_rt.pdf}
  \caption{
  Distance dependent portfolio effects as a function of straying rate $m$ and trait heritability $h^2$. When straying is distance dependent, $m$ increases as $\Delta\theta$ decreases.
  } \label{fig:mthetaPE}
\end{figure}

\begin{figure}
  \captionsetup{justification=raggedright,
singlelinecheck=false
}
\centering
\includegraphics[width=0.35\textwidth]{fig_relax_inertia.pdf}
\caption{
Distance dependent straying, where increased differences in trait optima between sites $\Delta\theta$ corresponds to lower rates of straying $m$.
At low rates of straying $m=0.02$ ($\Delta\theta=24$), extinction of the dominant population leads to slower-than-expected recovery times because the subordinate population is isolated enough to evolve towards its own trait optimum. %until growth of the dominant population overwhelms this local selection.
In this case, $m$ is less than $m=0.034$ (denoted by the asterisk in figure \ref{extfig-fig:mtheta}), such that isolation allows the subdominant population to `run away' from the influence of the dominant population, leading to a switch in states.
If $m$ is low but greater than $0.034$, isolation permits the subdominant population to `run away' from the influence of the dominant population, until it is overwhelmed by the recovering dominant population, and reverts back to its previous trait mean prior to the disturbance.
} \label{fig:inertia}
\end{figure}

\begin{figure*}
  \captionsetup{justification=raggedright,
singlelinecheck=false
}
  \centering
  \includegraphics[width=0.8\textwidth]{fig_relax_mtheta.pdf}
  \caption{
  Distance dependent recovery times for three disturbance types. When straying is distance dependent, $m$ increases as $\Delta\theta$ decreases for constant (a) and density-dependent (b) staying rates.
  The fold bifurcation is not as clear in (b) because $\Delta\theta$ is a function of the individual straying rate $m_0$, whereas the x-axis in (b) is the straying rate at the steady state $m^*$.
  Despite this difference, the general trends shown in (a) are also present in (b).
  } \label{fig:mthetamvm}
\end{figure*}

\begin{figure}
  \captionsetup{justification=raggedright,
singlelinecheck=false
}
\centering
\includegraphics[width=0.35\textwidth]{fig_relax_both_lowh.pdf}
\caption{
Near collapse of both populations with a low straying rate $m=0.1$ and low trait heritability $h^2=0.2$ (see figure \ref{extfig-fig:relax}a).
Black line marks the calculated point of recovery post-perturbation.
Trait optima are $\theta_1 = 10$ (blue population trajectory) and $\theta_2 = 5$ (red population).
} \label{fig:relaxtraj_bothlh}
\end{figure}
